A Graph Theory Based Approach to MDAO Problem Formulation

### 2013-04-18 graph_syntax.tex
working on formatting for SMO

	\begin{equation}
	\txt{deg}_u^-(v):V \to \mathbb{N}
	\end{equation} 
	and the \emph{lower indegree limit} as
	\begin{equation}
	\txt{deg}_l^-(v):V \to \mathbb{N}.
	\end{equation}
	These user-specified limits govern the number of connection edges that may be directed into a variable
	node for a valid graph. Consider a variable node $v$ with
	$\txt{deg}_u^-(v) = \txt{deg}_l^-(v) = 1$. In this case, $v$ must have exactly one
	incomming explicit edge or the graph is invalid. Two possiblities exist for voilating 
	these limit conditions: 
	\begin{description}
	  \item[hole: ] The number of incomming edges is less than the lower indegree limit:
		\begin{equation} \txt{deg}^-(v) < \txt{deg}_l^-(v) \label{e:hole} \end{equation}
		This represents a lack of information being supplied to the node.

  \item[collision: ] The number of incomming edges is greater than $ \txt{deg}_u^-(v)$. 
    \begin{equation} \txt{deg}^-(v) > \txt{deg}_u^-(v) \label{e:collision}\end{equation}
\end{description} 
	An algorithm for detecting and managing these violations if proposed in Sec.~\ref{s:building graphs}.\ref{ss:obtaining FPG}.

@@

\subsection{Analysis Blocks and Connections}
\label{ss:analysis blocks and connections}
Analysis tools take in a number input variables and then perform some work to calculate 
the values for their respective outputs. In an MDAO graph, this process is 
represented by a group of nodes and edges called an \emph{analysis block}, 
shown in Fig. \ref{f:analysis block}. Within an analysis block each variable 
node represents a single input or output and is connected 
to a single model node via a fixed edge. Note that in Fig.~\ref{f:analysis block}, 
the analysis block contains two model nodes, with a single edge connecting them. 
This edge represents the necessary calculations to map given inputs 
to proper output values. If constructing a weighted graph, the weight calculation edge 
provides the opportunity to computational cost. However, it is also allowed to skip 
this edge and have both incomming and outgoing edges to variables through a single model 
node for a given analysis block. Although analysis blocks are comprised of multiple nodes and edges, since all 
	the edges within them are fixed, they become fixed sub-graphs within a graph. In this way, they cannot be altered but they can be removed as a group.
\begin{figure}[htb!]
    \begin{center}
    \includegraphics[width=4in]{images/analysis_block}
    \end{center}
    \vspace{-10pt}
\caption{Example analysis block. The each node type and edge type is labeled in italics and annotated parenthetically.}
\label{f:analysis block}
\end{figure}

@@

  When solving a problem using a heirarchical decomposition approach, 
  there are various techniques for partitioning that are effective in different 
  scenarios \cite{krishnamachari1997optimal,michelena1997hypergraph,
  sobieszczanski1997,Perez2004,allison2009optimal}. Tosserams et al proposed a 
  language based syntax for describing the partitioning of problems, named $\Psi$
  \cite{tosserams2010specification}. $\Psi$ provides an opposing perspective to 
  this work, where they compose hierarchies from the bottom up, into larger and 
  larger groups. However, $\Psi$ provides a compiler that can produce a standard 
  problem representation of the assembled problem, and a number of example converters
  from that standard representation to application specific formats.

>>>>

  \begin{equation}
  \txt{deg}_u^-(v):V \to \mathbb{N}
  \end{equation} 
  and the \emph{lower indegree limit} as
  \begin{equation}
  \txt{deg}_l^-(v):V \to \mathbb{N}.
  \end{equation}
  These user-specified limits govern the number of connection edges that may 
  be directed into a variable node for a valid graph. Consider a variable 
  node $v$ with $\txt{deg}_u^-(v) = \txt{deg}_l^-(v) = 1$. In this case, $v$ 
  must have exactly one incomming explicit edge or the graph is invalid. 
  Two possiblities exist for voilating these limit conditions:

  \begin{description}
    \item[hole: ] The number of incomming edges is less than the lower indegree limit:
      \begin{equation} \txt{deg}^-(v) < \txt{deg}_l^-(v) \label{e:hole} \end{equation}
      This represents a lack of information being supplied to the node.
    \item[collision: ] The number of incomming edges is greater than $ \txt{deg}_u^-(v)$. 
      \begin{equation} \txt{deg}^-(v) > \txt{deg}_u^-(v) \label{e:collision}\end{equation}
  \end{description}

  An algorithm for detecting and managing these violations if proposed in Sec.~\ref{s:building graphs}.\ref{ss:obtaining FPG}.

@@

\subsection{Analysis Blocks and Connections}
\label{ss:analysis blocks and connections}
Analysis tools take in a number input variables and then perform some work to calculate 
the values for their respective outputs. In an MDAO graph, this process is 
represented by a group of nodes and edges called an \emph{analysis block}, 
shown in Fig. \ref{f:analysis block}. Within an analysis block each variable 
node represents a single input or output and is connected 
to a single model node via a fixed edge. Note that in Fig.~\ref{f:analysis block}, 
the analysis block contains two model nodes, with a single edge connecting them. 
This edge represents the necessary calculations to map given inputs 
to proper output values. If constructing a weighted graph, the weight calculation edge 
provides the opportunity to computational cost. However, it is also allowed to 
skip this edge and have both incomming and outgoing edges to variables through a 
single model node for a given analysis block. Although analysis blocks are 
comprised of multiple nodes and edges, since all the edges within them are 
fixed, they become fixed sub-graphs within a graph. In this way, they cannot be 
altered but they can be removed as a group.

\begin{figure}[htb!]
    \begin{center}
    \includegraphics[width=4in]{images/analysis_block}
    \end{center}
    \vspace{-10pt}
\caption{Example analysis block. The each node type and edge type is labeled in italics and annotated parenthetically.}
\label{f:analysis block}
\end{figure}

@@

  When solving a problem using a heirarchical decomposition approach, 
  there are various techniques for partitioning that are effective in different 
  scenarios \cite{krishnamachari1997optimal,michelena1997hypergraph,sobieszczanski1997,Perez2004,allison2009optimal}. 
  Tosserams et al proposed a language based syntax for describing the partitioning of problems, named $\Psi$
  \cite{tosserams2010specification}. $\Psi$ provides an opposing perspective to 
  this work, where they compose hierarchies from the bottom up, into larger and 
  larger groups. However, $\Psi$ provides a compiler that can produce a standard 
  problem representation of the assembled problem, and a number of example converters
  from that standard representation to application specific formats.

### 2013-04-18 problem_formulation.tex
writing update
fixing a few things to get it to compile
most of suggested major changes
updated introduction and started editing a couple of lower sections
updated the Desgin Variable, Objectives, Constraints section with some new notes. Two new node types
put in example problem using a new .tex file
split graph_syntax into two files
working on formatting for SMO

\documentclass[]{aiaa-tc} % insert '[draft]' option to show overfull boxes

 \title{An application of Graph Theory to MDAO problem formulation}

\author{
  David Pate, %
     \thanks{Georgia Tech}
  Dr. Brian German 
     \thanks{Georgia Tech...}
  Justin Gray,%
     \thanks{Aerospace Engineer, MDAO Branch, Mail Stop 5-11, AIAA Member}   
 }

@@

\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{caption} 
\usepackage{amsmath}
\usepackage{lscape}
\usepackage{hyperref}
\usepackage{appendix}
\usepackage[section]{placeins}

@@

@@

\input{intro}
\input{graph_syntax}

\section{Example Problem}

>>>>

\documentclass[referee]{svjour3} % insert '[draft]' option to show overfull boxes

 \title{A Graph Theory Based Approach to MDAO Problem Formulation}

\author{
  David Pate, %
  Justin Gray,%
  Dr. Brian German 
 }

 \institute { Justin Gray \at NASA Glenn Research Center, Mail Stop 5-11, 21000 Brookpark Rd Clevland OH 44135 %
  \and David Pate \at Gatech \and Dr. Brian German \at Gatech}

\journalname{Structrual and Multidisciplinary Optimization}

@@

\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{caption} 
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{lscape}
\usepackage{hyperref}
\usepackage{appendix}
\usepackage[section]{placeins}
\usepackage[retainorgcmds]{IEEEtrantools}
\usepackage{subfigure}
\usepackage{comment}
\usepackage{booktabs}

@@

\newcommand{\txt}{\textrm}

@@

\input{intro}
\input{graph_syntax}
\input{mcg_fpg}
\input{example_problem}
